`tidyfun`

### 2022-01-23 papers.Rmd
update papers

@@

J Wrobel$^\ddagger$, ML Martin, R Bakshi, PA Calabresi, M Elliot, D Roalf, RC Gur, RE Gur, RG Henry, G Nair, J Oh, N Papinutto, D Pelletier, Daniel Salo Reich, WD Rooney, TD Satterthwaite, W Stern, K Prabhakaran, NL Sicotte, RT Shinohara, \bf J. Goldsmith \rm (2020).
	Intensity warping for multisite MRI harmonization.
	<i> NeuroImage, </i> 
	<b>223</b> 117284.

@@

L R Mitrani, J De Los Santos, E Driggin, R Kogan, S Helmke, **J Goldsmith**, A B Biviano, M S Maurer (2020). 
	Anticoagulation with warfarin compared to novel oral anticoagulants for atrial fibrillation in adults with transthyretin cardiac amyloidosis: comparison of thromboembolic events and major bleeding
	<i> Amyloid, </i> 
	<b>28</b> 30-34.

H Rosenblum, A Masri, D L Narotsky, **J Goldsmith**, N Hamid, R T Hahn, S Kodali, T Vahl, T Nazif, O K Khalique, S Bokhari, P Soman, J L Cavalcante, M S Maurer, A Castano
	Unveiling outcomes in coexisting severe aortic stenosis and transthyretin cardiac amyloidosis (2020).
	<i> European Journal of Heart Failure, </i> 
	<b>23</b> 250-258.

@@

## 2015

@@

## 2014

@@

## 2013

@@

## 2012

@@

## 2011 and before

>>>>

## 2021

Yan, X., **Goldsmith, J.**, Mohan, S., Turnbull, Z.A., Freundlich, R.E., Billings, F.T., Kiran, R.P., Li, G. and Kim, M. (2021). 
	Impact of Intraoperative Data on Risk Prediction for Mortality After Intra-Abdominal Surgery. 
	_Anesthesia \& Analgesia_, **134** 102-113.

Saith, S.E., Gamino, D., Teruya, S., Guadalupe, S., Helmke, S., De Los Santos, J., **Goldsmith, J.**, Rosenblum, H.R., Griffin, J.M. and Maurer, M.S., (2021). 
	Factors associated with changes in serum transthyretin after treatment with tafamidis and outcomes in transthyretin cardiac amyloidosis.
	_Amyloid_, **28** 267-268.

Duran, A.T., Pascual, C.B., **Goldsmith, J.**, Howard, V.J., Hutto, B., Colabianchi, N., Vena, J.E., McDonnell, M.N., Blair, S.N., Hooker, S.P. and Diaz, K.M. (2021).
	Objectively Measured Physical Activity and Sedentary Time Among Adults With and Without Stroke: A National Cohort Study.
	_Stroke_, **52** e729-e732.

Navas-Acien, A., Domingo-Relloso, A., Subedi, P., Riffo-Campos, A.L., Xia, R., Gomez, L., Haack, K., **Goldsmith, J.**, Howard, B.V., Best, L.G. and Devereux, R., (2021). 
	Blood DNA Methylation and Incident Coronary Heart Disease: Evidence From the Strong Heart Study. 
	_JAMA Cardiology_, **6** 1237-1246.

Johnson, C.N., Ramphal, B., Koe, E., Raudales, A., **Goldsmith, J.** and Margolis, A.E., (2021). 
	Cognitive correlates of autism spectrum disorder symptoms. 
	_Autism Research_, **14** 2405-2411.

Margolis, A.E., Ramphal, B., Pagliaccio, D., Banker, S., Selmanovic, E., Thomas, L.V., Factor-Litvak, P., Perera, F., Peterson, B.S., Rundle, A. Herbstman, J.B., **Goldsmith, J.**, and Rauh, V. (2021). 
	Prenatal exposure to air pollution is associated with childhood inhibitory control and adolescent academic achievement. 
	_Environmental Research_, **202** p 111570.

Nunez, Y., Boehme, A.K., Li, M., **Goldsmith, J.**, Weisskopf, M.G., Re, D.B., Navas-Acien, A., van Donkelaar, A., Martin, R.V. and Kioumourtzoglou, M.A., (2021). 
	Parkinson's disease aggravation in association with fine particle components in New York State. 
	_Environmental Research_, **201**, p.111554.

Cornelius, T., Denes, A., Webber, K.T., Guest, C., **Goldsmith, J.**, Schwartz, J.E., and Gorin, A.A. (2021).
	Relationship quality and objectively measured physical activity before and after implementation of COVID-19 stay-home orders.
	_Journal of Health Psychology_, DOI:13591053211042075.

C P Friel, C B Pascual, A T Duran, **J Goldsmith**, K M Diaz (2021).
	Joint associations of occupational standing and occupational exertion with musculoskeletal symptoms in a US national sample.
	_Occupational and Environmental Medicine_, **78**, 494-499.

Rowland, S.T., Parks, R.M., Boehme, A.K., **Goldsmith, J.**, Rush, J., Just, A.C. and Kioumourtzoglou, M.A., (2021). 
	The association between ambient temperature variability and myocardial infarction in a New York-State-based case-crossover study: An examination of different variability metrics. 
	_Environmental Research_, **197**, p.111207.

McDonnell, E.I., Zipunnikov, V., Schrack, J.A., **Goldsmith, J.** and Wrobel, J., (2021). 
	Registration of 24-hour accelerometric rest-activity profiles and its application to human chronotypes. 
	_Biological Rhythm Research_, pp.1-21.

Krakauer, J.W., Kitago, T., **Goldsmith, J.**, Ahmad, O., Roy, P., Stein, J., Bishop, L., Casey, K., Valladares, B., Harran, M.D. and Cortes, J.C. (2021). 
	Comparing a Novel Neuroanimation Experience to Conventional Therapy for High-Dose Intensive Upper-Limb Training in Subacute Stroke: The SMARTS2 Randomized Trial. 
	_Neurorehabilitation and Neural Repair_, **35**, pp.393-405.

**J Goldsmith**, Y Sun, L Fried, J Wing, G W Miller, K Berhane (2021).
	The Emergence and Future of Public Health Data Science.
	_Public Health Reviews_, ** accepted.

Nunez, Y., Gibson, E.A., Tanner, E.M., Gennings, C., Coull, B.A., **Goldsmith, J.**, and Kioumourtzoglou, M.A., (2021). 
	Reflection on modern methods: good practices for applied statistical learning in epidemiology. 
	_International journal of epidemiology_, **50**, 685-693.

H Rosenblum, A Masri, D L Narotsky, **J Goldsmith**, N Hamid, R T Hahn, S Kodali, T Vahl, T Nazif, O K Khalique, S Bokhari, P Soman, J L Cavalcante, M S Maurer, A Castano
	Unveiling outcomes in coexisting severe aortic stenosis and transthyretin cardiac amyloidosis (2021).
	_European Journal of Heart Failure_, **23** 250-258.

L R Mitrani, J De Los Santos, E Driggin, R Kogan, S Helmke, **J Goldsmith**, A B Biviano, M S Maurer (2021).
	Anticoagulation with warfarin compared to novel oral anticoagulants for atrial fibrillation in adults with transthyretin cardiac amyloidosis: comparison of thromboembolic events and major bleeding
	_Amyloid_, **28** 30-34.

S Lovinsky-Desir, K H Jung, M Montilla, J Quinn, J Cahill, D Sheehan, F Perera, S N Chillrud, **J Goldsmith**, M Perzanowski, A Rundle, R Miller (2021).
	Locations of Adolescent Physical Activity in an Urban Environment and their Associations with Air Pollution and Lung Function.
	_Annals of the American Thoracic Society_, **18** 84-92.

@@

J Wrobel$^\ddagger$, ML Martin, R Bakshi, PA Calabresi, M Elliot, D Roalf, RC Gur, RE Gur, RG Henry, G Nair, J Oh, N Papinutto, D Pelletier, Daniel Salo Reich, WD Rooney, TD Satterthwaite, W Stern, K Prabhakaran, NL Sicotte, RT Shinohara, **J Goldsmith** (2020).
	Intensity warping for multisite MRI harmonization.
	<i> NeuroImage, </i> 
	<b>223</b> 117284.

@@

@@

## 2015 and before

@@

@@

@@

@@
